### 2020-02-18 Article.tex
Trees

During this section we want to study
the asymptotic probability that the 
$r$-neighborhood of a given vertex $v\in \N$
in $G_n$ 
is a tree that belongs to a given $k$-equivalence
class of trees $\mathcal{T}$ with radius at most
$r$. That is, we want to know
\[\Ln \mathrm{Pr}\big( 
T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
\]
Denote this limit by $\mathrm{Pr}[r,\mathcal{T}]$. Notice that the 
definition of  $\mathrm{Pr}[r,\mathcal{T}]$ does not depend by the
choice of $v$.\par

@@

>>>>

During this section we want to study
the asymptotic probability that the 
$r$-neighborhood of a given vertex $v\in \N$
in $G_n$ 
is a tree that belongs to a given $k$-equivalence
class of trees $\mathcal{T}$ with radius at most
$r$. That is, we want to know
\[\Ln \mathrm{Pr}\big( 
T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
\]

Denote this limit by $\mathrm{Pr}[r,\mathcal{T}]$. Notice that the 
definition of  $\mathrm{Pr}[r,\mathcal{T}]$ does not depend by the
choice of $v$.\par

@@

\begin{definition}
	We call an hypergraph $G$ \textbf{saturated} if any proper 
	sub-hypergraph $G^\prime \subset H$ satisfies $ex(G^\prime)<ex(G)$. \par
	The \textbf{center} of a connected hypergraph $G$ is the maximal saturated
	sub-hypergraph and it is denoted by $Center(G)$. In the general case 
	the center of an hypergraph is the union of the
	centers of its connected components. 
\end{definition}

\begin{definition}
	Let $G$ be a connected hypergraph and let $\overline{v}\in V(G)^*$.
	Then we call $Center(G, \overline{v})$ to the minimal connected hypergraph
	that contains $Center(G)$ and the vertices $\overline{v}$. In general, if 
	$G$ is an arbitrary hypergraph with connected components $G_1, \dots, G_k$,
	and $\overline{v}$ are vertices $V(G)$, then we call 
	$Center(G, \overline{v})$ to the union of $Center(G_i, V(G_i)\cap
	\overline{v})$ for all the connected components $G_i$.
\end{definition}

\begin{definition}
	Let $G$ be an hypergraph $G$, let $\overline{u}\in V(G)^*$
	and let $v\in V(G)$.
	Consider the graph $G^\prime= G\setminus 
	E\big(Center(G,\overline{u})\big)$. Then the connected components of
	$G^\prime$ are all trees. We call the \textbf{tree of $v$ in
	$G(\overline{u})$}, denoted by $Tree(G\big(\overline{u}),v\big)$,
	to the connected component of $G^\prime$ to which $v$ belongs
	with $v$ as its root. \par   
\end{definition}
